# Ensemble Machine Learning

_Rachael Phillips_

Based on the [`sl3` `R` package](https://github.com/tlverse/sl3) by _Jeremy
Coyle, Nima Hejazi, Ivana Malenica, and Oleg Sofrygin_.

Updated: `r Sys.Date()`

## Learning Objectives
By the end of this lesson you will be able to:

1. Assemble an ensemble of learners based on the properties that identify what
   features they support.
2. Customize learner hyperparameters to incorporate a diversity of different
   settings.
3. Select a subset of available covariates and pass only those variables to the
   modeling algorithm.
4. Fit an ensemble with nested cross-validation to obtain an estimate of the
   performance of the ensemble itself.
5. Calculate `sl3` variable importance metrics.
6. Interpret the discrete and continuous super learner fits.
7. Rationalize the need to remove bias from the super learner to make an optimal
   bias-variance tradeoff for the parameter of interest.

## Introduction

Now that we have defined the statistical estimation problem in [The Targeted
Learning Roadmap](#intro), we are ready construct the TMLE; an asymptotically
efficient substitution estimator of this target quantity.

The first step in this estimation procedure is an initial estimate of the
data-generating distribution, or the relevant part of this distribution that is
needed to evaluate the target parameter. For this initial estimation, we use the
super learner [@vdl2007super], an important step for creating a robust
estimator.

#### Super Learner {-}

* Loss-function-based tool that uses V-fold cross-validation to obtain the best
  prediction of the relevant part of the likelihood that's needed to evaluate
  target parameter.

* Requires expressing the estimand as the minimizer of an expected loss, and
  proposing a library of algorithms ("learners" in `sl3` nomenclature) that we
  think might be consistent with the true data-generating distribution.

* Proven to be asymptotically as accurate as the best possible prediction
  algorithm that is tested [@vdl2003unified; @van2006oracle].

* The *discrete super learner*, or cross-validated selector, is the algorithm in
  the library that minimizes the V-fold cross-validated empirical risk.

* The *continuous super learner* is a weighted average of the library of
  algorithms, where the weights are chosen to minimize the V-fold
  cross-validated empirical risk of the library. Restricting the weights
  ("metalearner" in `sl3` nomenclature) to be positive and sum to one (convex
  combination) has been shown to improve upon the discrete super learner
  [@polley2010super; @vdl2007super].

 * This background material is described in greater detail in the accompanying
   `tlverse` handbook [`sl3`
   chapter](https://tlverse.org/tlverse-handbook/ensemble-machine-learning.html).

## Basic `sl3` Implementation

We begin by illustrating the core functionality of the super learner algorithm
as implemented in `sl3`.

The `sl3` implementation consists of the following steps:

0. Load the necessary libraries and data
1. Define the machine learning task
2. Make a super learner by creating library of base learners and a metalearner
3. Train the super learner on the machine learning task
4. Obtain predicted values

### WASH Benefits Study Example {-}

Using the WASH data, we are interested in predicting weight-for-height z-score
`whz` using the available covariate data.

### 0. Load the necessary libraries and data {-}

```{r setup, message=FALSE, warning=FALSE}
library(kableExtra)
library(knitr)
library(skimr)
library(tidyverse)
library(data.table)
library(sl3)
library(SuperLearner)
library(origami)

set.seed(7194)

# load data set and take a peek
washb_data <- fread("https://raw.githubusercontent.com/tlverse/tlverse-data/master/wash-benefits/washb_data.csv",
  stringsAsFactors = TRUE
)

head(washb_data) %>%
  kable(digits = 4) %>%
  kable_styling(fixed_thead = T, font_size = 10) %>%
  scroll_box(width = "100%", height = "250px")
```

### 1. Define the machine learning task {-}

To define the machine learning **"task"** (predict weight-for-height z-score
`whz` using the available covariate data), we need to create an `sl3_Task`
object.

The `sl3_Task` keeps track of the roles the variables play in the
machine learning problem, the data, and any metadata (e.g., observational-level
weights, id, offset).

```{r task}
# specify the outcome and covariates
outcome <- "whz"
covars <- colnames(washb_data)[-which(names(washb_data) == outcome)]

# create the sl3 task
washb_task <- make_sl3_Task(
  data = washb_data,
  covariates = covars,
  outcome = outcome
)

# examine the task
washb_task
```

### 2. Make a super learner {-}

Now that we have defined our machine learning problem with the task, we are
ready to **"make"** the super learner. This requires specification of

* Base learning algorithms, to establish a library of learners that we think
might be consistent with the true data-generating distribution.
* Metalearner, to ensemble the base learners.

We might also incorporate

* Feature selection, to pass only a subset of the predictors to the algorithm.
* Hyperparameter specification, to tune base learners.

Learners have properties that indicate what features they support. We may use
`sl3_list_properties()` to get a list of all properties supported by at least
one learner.

```{r list-properties}
sl3_list_properties()
```
Since we have a continuous outcome, we may identify the learners that support
this outcome type with `sl3_list_learners()`.

```{r list-learners}
sl3_list_learners(c("continuous"))
```

Now that we have an idea of some learners, we can construct them using the
`make_learner` function.

```{r baselearners}
# choose base learners
lrnr_glm <- make_learner(Lrnr_glm)
lrnr_mean <- make_learner(Lrnr_mean)
lrnr_glmnet <- make_learner(Lrnr_glmnet)
```
We can customize learner hyperparameters to incorporate a diversity of different
settings.

Documentation for the learners and their hyperparameters can be found
in the [`sl3` Learners
Reference](https://tlverse.org/sl3/reference/index.html#section-sl-learners).

We can also include learners from the `SuperLearner` `R` package.

```{r extra-lrnr}
lrnr_ranger100 <- make_learner(Lrnr_ranger, num.trees = 100)
lrnr_hal_simple <- make_learner(Lrnr_hal9001, degrees = 1, n_folds = 2)
lrnr_gam <- Lrnr_pkg_SuperLearner$new("SL.gam")
lrnr_bayesglm <- Lrnr_pkg_SuperLearner$new("SL.bayesglm")
```

In order to assemble the library of learners, we need to **"stack"** them
together.

A `Stack` is a special learner and it has the same interface as all
other learners. What makes a stack special is that it combines multiple learners
by training them simultaneously, so that their predictions can be either
combined or compared.

```{r stack}
stack <- make_learner(
  Stack,
  lrnr_glm, lrnr_mean, lrnr_ranger100, lrnr_glmnet,
  lrnr_gam, lrnr_bayesglm
)
```

We will fit a non-negative least squares metalearner using `Lrnr_nnls`. Note
that any learner can be used as a metalearner.

```{r metalearner}
metalearner <- make_learner(Lrnr_nnls)
```
We can optionally select a subset of available covariates and pass only
those variables to the modeling algorithm.

Let's consider screening covariates based on their correlation with our outcome
of interest (`cor.test` p-value $\leq 0.1$).

```{r screener}
screen_cor <- Lrnr_pkg_SuperLearner_screener$new("screen.corP")
# which covariates are selected on the full data?
screen_cor$train(washb_task)
```
To **"pipe"** only the selected covariates to the modeling algorithm, we need to
make a `Pipeline`, which is a just set of learners to be fit sequentially, where
the fit from one learner is used to define the task for the next learner.

```{r screener-pipe}
cor_pipeline <- make_learner(Pipeline, screen_cor, stack)
```
Now our learners will be preceded by a screening step.

We also consider the original `stack`, just to compare how the feature selection
methods perform in comparison to the methods without feature selection.

Analogous to what we have seen before, we have to stack the pipeline and
original `stack` together, so we may use them as base learners in our super
learner.

```{r screeners-stack}
fancy_stack <- make_learner(Stack, cor_pipeline, stack)
# we can visualize the stack
dt_stack <- delayed_learner_train(fancy_stack, washb_task)
plot(dt_stack, color = FALSE, height = "400px", width = "100%")
```

We have made a library/stack of base learners and a metalearner, so we
are ready to make the super learner. The super learner algorithm fits a
metalearner on the validation-set predictions.

```{r make-sl}
sl <- make_learner(Lrnr_sl,
  learners = fancy_stack,
  metalearner = metalearner
)
# we can visualize the super learner
dt_sl <- delayed_learner_train(sl, washb_task)
plot(dt_sl, color = FALSE, height = "400px", width = "100%")
```

### 3. Train the super learner on the machine learning task {-}

Now we are ready to **"train"** our super learner on our `sl3_task` object, `washb_task`.

```{r sl-basic}
sl_fit <- sl$train(washb_task)
```

### 4. Obtain predicted values {-}

Now that we have fit the super learner, we are ready to obtain our predicted
values, and we can also obtain a summary of the results.

```{r sl-basic-summary}
sl_preds <- sl_fit$predict()
head(sl_preds)
sl_fit$print()
```
## Extensions

### Cross-validated Super Learner

We can cross-validate the super learner to see how well the super learner
performs on unseen data, and obtain an estimate of the cross-validated risk of
the super learner.

This estimation procedure requires an "external" layer of cross-validation,
also called nested cross-validation, which involves setting aside a separate
holdout sample that we don’t use to fit the super learner. This
external cross validation procedure may also incorporate 10 folds, which is the
default in `sl3`. However, we will incorporate 2 outer/external folds of
cross-validation for computational efficiency.

We also need to specify a loss function to evaluate super learner.
Documentation for the available loss functions can be found in the [`sl3` Loss
Function Reference](https://tlverse.org/sl3/reference/loss_functions.html).

```{r CVsl}
washb_task_new <- make_sl3_Task(
  data = washb_data,
  covariates = covars,
  outcome = outcome,
  folds = make_folds(washb_data, fold_fun = folds_vfold, V = 2)
)
CVsl <- CV_lrnr_sl(sl_fit, washb_task_new, loss_squared_error)
CVsl %>%
  kable(digits = 4) %>%
  kable_styling(fixed_thead = T, font_size = 10) %>%
  scroll_box(width = "100%", height = "250px")
```

### Variable Importance Measures with `sl3`

The `sl3` `varimp` function returns a table with variables listed in decreasing
order of importance, in which the measure of importance is based on a risk
difference between the learner fit with a permuted covariate and the learner
fit with the true covariate, across all covariates.

In this manner, the larger the risk difference, the more important the variable
is in the prediction.

```{r varimp}
washb_varimp <- varimp(sl_fit, loss_squared_error)
washb_varimp %>%
  kable(digits = 4) %>%
  kable_styling(fixed_thead = T, font_size = 10) %>%
  scroll_box(width = "100%", height = "250px")
```

## Exercise

### Predicting Myocardial Infarction with `sl3`

Follow the steps below to predict myocardial infarction (`mi`) using the
available covariate data. Thanks to Professor David Benkeser at Emory University
for making the this Cardiovascular Health Study (CHS) data accessible.

Work with a buddy/team. You have 20 minutes.

In the [etherpad](https://etherpad.net/p/acic2019-tlverse), submit your group's
answers to the following questions.

1. Which learner was the discrete super learner? What was the cross validated
mean risk of the discrete super learner?
2. What was the cross validated risk of the continuous super learner?
3. Did your group face any challenges?
4. Any additional comments/questions about this `sl3` section of the workshop?

```{r ex-setup, message=FALSE, warning=FALSE}
# load the data set
db_data <-
  url("https://raw.githubusercontent.com/benkeser/sllecture/master/chspred.csv")
chspred <- read_csv(file = db_data, col_names = TRUE)
# take a quick peek
head(chspred) %>%
  kable(digits = 4) %>%
  kable_styling(fixed_thead = T, font_size = 10) %>%
  scroll_box(width = "100%", height = "200px")
```

1. Create an `sl3` task, setting myocardial infarction `mi` as the outcome and
   using all available covariate data.
2. Make a library of seven relatively fast base learning algorithms (i.e., do
   not consider BART or HAL). Customize hyperparameters for one of your
   learners. Feel free to use learners from `sl3` or `SuperLearner`. You may
   use the same base learning library that is presented above.
3. Incorporate feature selection with the `SuperLearner` screener `screen.corP`.
4. Fit the metalearning step with non-negative least squares, `Lrnr_nnls`.
5. With the metalearner and base learners, make the super learner and train it
   on the task.
6. Print your super learner fit by calling `print()` with `$`.
7. Cross-validate your super learner fit to see how well it performs on unseen
   data. Specify `loss_squared_error` as the loss function to evaluate the
   super learner. Like above, create a new task with 2 folds of external cross
   validation for computational efficiency.

## Summary

* The general ensemble learning approach of super learner can be applied to a
  diversity of estimation and prediction problems that can be defined by a loss
  function.

* Plug-in estimators of the estimand are desirable because a plug-in estimator
  respects both the local and global constraints of the statistical model.

* Asymptotically linear estimators are also advantageous, since they converge to
  the estimand at $\frac{1}{\sqrt{n}}$ rate, and thereby permit formal
  statistical inference.

* If we plug in the estimator returned by super learner into the target
  parameter mapping, then we would end up with an estimator that has the same
  bias as what we plugged in. This estimator would not be asymptotically linear.

* Targeted maximum likelihood estimation (TMLE) is a general strategy that
  succeeds in constructing asymptotically linear plug-in estimators.

* In the chapters that follow, we focus on the targeted maximum likelihood
  estimator and the targeted minimum loss-based estimator, both referred to as
  TMLE.
