# Super (Machine) Learning {#sl3}

Based on the [`sl3` `R` package](https://github.com/tlverse/sl3) by _Jeremy
Coyle, Nima Hejazi, Ivana Malenica, and Oleg Sofrygin_.

Updated: `r Sys.Date()`

## Learning Objectives
By the end of this chapter you will be able to:

1. Select a loss function that is appropriate for the functional parameter to be
   estimated.
2. Assemble an ensemble of learners based on the properties that identify what
   features they support.
3. Customize learner hyperparameters to incorporate a diversity of different
   settings.
4. Select a subset of available covariates and pass only those variables to the
   modeling algorithm.
5. Fit an ensemble with nested cross-validation to obtain an estimate of the
   performance of the ensemble itself.
6. Obtain `sl3` variable importance metrics.
7. Interpret the discrete and continuous Super Learner fits.
8. Rationalize the need to remove bias from the Super Learner to make an optimal
   bias–variance tradeoff for the parameter of interest.

## Motivation

- A common task in statistical data analysis is estimator selection (e.g., for 
  prediction).
- There is no universally optimal machine learning algorithm for density 
  estimation or prediction.
- For some data, one needs learners that can model a complex function.
- For others, possibly as a result of noise or insufficient sample size, a 
  simple, parametric model might fit best.
- The Super Learner, an ensemble learner, solves this issue, by allowing a
  combination of learners from the simplest (intercept-only) to most complex
  (neural nets, random forests, SVM, etc).
- It works by using cross-validation in a manner which guarantees that the
  resulting fit will be as good as possible, given the learners provided. 

## Introduction

In [Chapter 1](#intro), we introduced the Roadmap for Targeted Learning as a
general template to translate real-world data applications into formal
statistical estimation problems. The first steps of this roadmap define the
*statistical estimation problem*, which establish

1. Data as a realization of a random variable, or equivalently, an outcome of a
   particular experiment.
2. A statistical model, representing the true knowledge about the
   data-generating experiment.
3. A translation of the scientific question, which is often causal, into a
   target parameter.

Note that if the target parameter is causal, step 3 also requires
establishing identifiability of the target quantity from the observed data
distribution, under possible non-testable assumptions that may not necessarily
be reasonable. Still, the target quantity does have a valid statistical
interpretation. See [causal target parameters](#causal) for more detail on
causal models and identifiability.

Now that we have defined the statistical estimation problem, we are ready to
construct the TMLE; an asymptotically linear and efficient substitution
estimator of this target quantity. The first step in this estimation procedure
is an initial estimate of the data-generating distribution, or the relevant part
of this distribution that is needed to evaluate the target parameter. For this
initial estimation, we use the *Super Learner* [@vdl2007super]. 

The Super Learner provides an important step in creating a robust estimator. It 
is a loss-function-based tool that uses cross-validation to obtain the best
prediction of our target parameter, based on a weighted average of a library of
machine learning algorithms. 

The library of machine learning algorithms consists of functions ("learners" in
the `sl3` nomenclature) that we think might be consistent with the true 
data-generating distribution (i.e. algorithms selected based on contextual 
knowledge of the experiment that generated the data). Also, the library should  
contain a large set of "default" algorithms that may range from a simple linear 
regression model to multi-step algorithms involving screening covariates, 
penalizations, optimizing tuning parameters, etc. 

The ensembling of the collection of algorithms with weights ("metalearning" in 
the `sl3` nomenclature) has been shown to be adaptive and robust, even in small 
samples [@polley2010super]. The Super Learner is proven to be asymptotically as 
accurate as the best possible prediction algorithm in the library 
[@vdl2003unified; @van2006oracle].

### Background

**Defining the loss function**

- A *loss function* ($L$) is defined as a function of the observed data and a
  candidate parameter value $\psi$, which has unknown true value $\psi_0$,
  $L(\psi)(O)$. 

- We can estimate the loss by substituting the empirical
  distribution $P_n$ for the true (but unknown) distribution of the observed data
  $P_0$. 
  
- A valid loss function will have expectation (risk) that is minimized at
  the true value of the parameter $\psi_0$. For example, the conditional mean
  minimizes the risk of the squared error loss. Thus, it is a valid loss function
  when estimating the conditional mean.
  
**What is cross-validation and how does it work?**

- There are many different cross-validation schemes, designed to accommodate different 
  study designs and data structures.
- The figure below shows an example of 10-fold cross-validation.  
  
```{r cv_fig, fig.show="hold", echo = FALSE}
knitr::include_graphics("img/misc/vs.pdf")
```  

- The *cross-validated empirical risk* of an algorithm is defined as the empirical 
  mean over a validation sample of the loss of the algorithm fitted on the 
  training sample, averaged across the splits of the data.
  
- Cross-validation is proven to be optimal for selection among estimators. This 
  result was established through the oracle inequality for the cross-validation 
  selector among a collection of candidate estimators [@vdl2003unified; 
  @van2006oracle]. The only condition is that loss function is uniformly bounded, 
  which is guaranteed in `sl3`.  
  
**Discrete vs. Continuous Super Learner**

- The *discrete Super Learner*, or *cross-validation selector*, is the algorithm
  in the library that minimizes the cross-validated empirical risk. 

- The *continuous/ensemble Super Learner*, often referred to as *Super Learner* 
  is a weighted average of the library of algorithms, where the weights are chosen 
  to minimize the cross-validated empirical risk of the library. 
  
- Restricting the weights to be positive and sum to one (i.e., a convex combination) has been 
  shown to improve upon the discrete Super Learner [@polley2010super; 
  @vdl2007super]. This notion of weighted combinations was introduced in 
  @wolpert1992stacked for neural networks and adapted for regressions in 
  @breiman1996stacked.

<!--
The *oracle results* prove that, if the number of algorithms in the library are
polynomial in sample size, then the cross-validation selector (i.e., discrete
Super Learner) (1) is equivalent with the oracle selector asymptotically (based
on sample of size of training samples), or (2) achieves the parametric rate (log
$n/n$) for convergence with respect to the loss-based dissimilarity (risk)
between a candidate estimate $\psi$ and the true parameter value $\psi_0$.
-->

#### Example: Super Learner for Prediction

- We observe a learning data set $X_i=(Y_i,W_i)$, for $i=1, ..., n$.
- Here, $Y_i$ is the outcome of interest, and $W_i$ is a p-dimensional 
  set of covariates.
- Our objective is to estimate the function $\psi_0(W) = E(Y|W)$.
- This function can be expressed as the minimizer of the expected loss:
  $\psi_0(W) = \text{argmin}_{\psi} E[L(X,\psi(W))]$.
- Here, the loss function is represented as $L$ (e.g., squared error loss,
  $L: (Y-\psi(W))^2)$).

#### General Overview of the Algorithm

**General step-by-step overview of the Super Learner algorithm:**

- Break up the sample evenly into $V$-folds (say $V$=10).
- For each of these 10 folds, remove that portion of the sample (kept out as
  validation sample) and the remaining will be used to fit learners (training
  sample).
- Fit each learner on the training sample (note, some learners will have their
  own internal cross-validation procedure or other methods to select tuning
  parameters).
- For each observation in the corresponding validation sample, predict the outcome
  using each of the learners, so if there are $p$ learners, then there would be
  $p$ predictions.
- Take out another validation sample and repeat until each of the $V$-sets of data
  are removed.
- Compare the cross-validated fit of the learners across all observations based
  on specified loss function (e.g., squared error, negative log-likelihood, etc.)
  by calculating the corresponding average loss (risk).
- Either:

  + choose the learner with smallest risk and apply that learner to entire data
    set (resulting SL fit),
  + do a weighted average of the learners to minimize the cross-validated risk
    (construct an ensemble of learners), by

    + re-fitting the learners on the original data set, and
    + use the weights above to get the SL fit.

This entire procedure can be itself cross-validated to get a consistent 
estimate of the future performance of the Super Learner, and we implement this 
procedure later in this chapter. 

```{r cv_fig2, echo = FALSE}
knitr::include_graphics("img/misc/SLKaiserNew.pdf")
``` 

### Why use the Super Learner?

- For prediction, one can use the cross-validated risk to empirically determine
  the relative performance of SL and competing methods. 
- When we have tested different algorithms on actual
  data and looked at the performance (e.g., MSE of prediction), never does one
  algorithm always win (see below).
- Below shows the results of such a study, comparing the fits of several different learners, 
  including the SL algorithms.

```{r cv_fig3, echo = FALSE}
knitr::include_graphics("img/misc/ericSL.pdf")
```

- Super Learner performs asymptotically as well as best possible weighted 
  combination. 
- By including all competitors in the library of candidate estimators (glm, neural nets, 
  SVMs, random forest, etc.), the Super Learner will asymptotically outperform 
  any of its competitors- even if the set of competitors is allowed to grow polynomial
  in sample size. 
- Motivates the name "Super Learner": it provides a system of combining many estimators
  into an improved estimator. 
  
For more detail on Super Learner we refer the reader to @vdl2007super and
@polley2010super. The optimality results for the cross-validation selector
among a family of algorithms were established in @vdl2003unified and extended
in @van2006oracle.
  
## `sl3` "Microwave Dinner" Implementation

We begin by illustrating the core functionality of the Super Learner algorithm
as implemented in `sl3`. For those who are interested in the internals 
of `sl3`, see this [`sl3` introductory 
tutorial](https://tlverse.org/sl3/articles/intro_sl3.html). 

The `sl3` implementation consists of the following steps:

0. Load the necessary libraries and data
1. Define the machine learning task
2. Make a Super Learner by creating library of base learners and a metalearner
3. Train the Super Learner on the machine learning task
4. Obtain predicted values

### WASH Benefits Study Example {-}

Using the WASH data, we are interested in predicting weight-for-height z-score
`whz` using the available covariate data. Let's begin!

### 0. Load the necessary libraries and data {-}

First, we will load the relevant `R` packages, set a seed, and load the data.

```{r setup, message=FALSE, warning=FALSE}
library(here)
library(data.table)
library(knitr)
library(kableExtra)
library(tidyverse)
library(origami)
library(SuperLearner)
library(sl3)

set.seed(7194) 
# my lucky seed! or is it 9174? or 4917? many lucky seeds, thanks lysdexia!

# load data set and take a peek
washb_data <- fread("https://raw.githubusercontent.com/tlverse/tlverse-data/master/wash-benefits/washb_data.csv",
                    stringsAsFactors = TRUE)
head(washb_data) %>%
  kable(digits = 4) %>%
  kableExtra:::kable_styling(fixed_thead = T) %>%
  scroll_box(width = "100%", height = "300px")
```

### 1. Define the machine learning task {-}

To define the machine learning **"task"** (predict weight-for-height z-score `whz`
using the available covariate data), we need to create an `sl3_Task` object. 

The `sl3_Task` keeps track of the roles the variables play in the
machine learning problem, the data, and any metadata (e.g., observational-level
weights, id, offset). 

Also, if we had missing outcomes, we would need to set 
`drop_missing_outcome = TRUE` when we create the task. 

```{r task}
# specify the outcome and covariates
outcome <- "whz"
covars <- colnames(washb_data)[-which(names(washb_data) == outcome)]

# create the sl3 task
washb_task <- make_sl3_Task(
  data = washb_data,
  covariates = covars,
  outcome = outcome
)
```
*This warning is important.* The task just imputed missing covariates for us.
Specifically, for each covariate column with missing values, `sl3` uses the
median to impute missing continuous covariates, and the mode to impute binary 
and categorical covariates. 

Also, for each covariate column with missing values, `sl3` adds an additional 
column indicating whether or not the value was imputed, which is particularly 
handy when the missingness in the data might be informative.

Also, notice that we did not specify the number of folds, or the loss function
in the task. The default cross-validation scheme is $V$-fold, with the number of
folds $V=10$.

Let's visualize our `washb_task`.

```{r task-examine}
washb_task
```

### 2. Make a Super Learner {-}

Now that we have defined our machine learning problem with the task, we are
ready to **"make"** the Super Learner. This requires specification of

* A library of base learning algorithms that we think might be consistent with
  the true data-generating distribution.
* A metalearner, to ensemble the base learners.

We might also incorporate

* Feature selection, to pass only a subset of the predictors to the algorithm.
* Hyperparameter specification, to tune base learners.

Learners have properties that indicate what features they support. We may use
`sl3_list_properties()` to get a list of all properties supported by at least
one learner.

```{r list-properties}
sl3_list_properties()
```
Since we have a continuous outcome, we may identify the learners that support
this outcome type with `sl3_list_learners()`.

```{r list-learners}
sl3_list_learners("continuous")
```

Now that we have an idea of some learners, we can construct them using the
`make_learner` function.

```{r baselearners}
# choose base learners
lrnr_glm <- make_learner(Lrnr_glm)
lrnr_mean <- make_learner(Lrnr_mean)
```
We can customize learner hyperparameters to incorporate a diversity of different
settings. Documentation for the learners and their hyperparameters can be found
in the [`sl3` Learners
Reference](https://tlverse.org/sl3/reference/index.html#section-sl-learners).

```{r extra-lrnr-awesome, message=FALSE, warning=FALSE}
lrnr_ranger50 <- make_learner(Lrnr_ranger, num.trees = 50)
lrnr_hal_simple <- make_learner(Lrnr_hal9001, max_degree = 2, n_folds = 2)
lrnr_lasso <- make_learner(Lrnr_glmnet) # alpha default is 1
lrnr_ridge <- make_learner(Lrnr_glmnet, alpha = 0)
lrnr_elasticnet <- make_learner(Lrnr_glmnet, alpha = .5)
```

We can also include learners from the `SuperLearner` `R` package.

```{r extra-lrnr-woah, message=FALSE, warning=FALSE}
lrnr_bayesglm <- Lrnr_pkg_SuperLearner$new("SL.bayesglm")
```

Here is a fun trick to create customized learners over a grid of parameters.

```{r extra-lrnr-svm, eval = FALSE}
# I like to crock pot my super learners
grid_params <- list(cost = c(0.01, 0.1, 1, 10, 100, 1000),
                    gamma = c(0.001, 0.01, 0.1, 1),
                    kernel = c("polynomial", "radial", "sigmoid"),
                    degree = c(1, 2, 3))
grid <- expand.grid(grid_params, KEEP.OUT.ATTRS = FALSE)
params_default <- list(nthread = getOption("sl.cores.learners", 1))
svm_learners <- apply(grid, MARGIN = 1, function(params_tune) {
  do.call(Lrnr_svm$new, c(params_default, as.list(params_tune)))})
```
```{r extra-lrnr-xgboost}
grid_params <- list(max_depth = c(2, 4, 6, 8),
                    eta = c(0.001, 0.01, 0.1, 0.2, 0.3),
                    nrounds = c(20, 50))
grid <- expand.grid(grid_params, KEEP.OUT.ATTRS = FALSE)
params_default <- list(nthread = getOption("sl.cores.learners", 1))
xgb_learners <- apply(grid, MARGIN = 1, function(params_tune) {
  do.call(Lrnr_xgboost$new, c(params_default, as.list(params_tune)))})
```

Did you see `Lrnr_caret` when we called `sl3_list_learners(c("continuous"))`? 
All we need to specify is the algorithm to use, which is passed as `method` to 
`caret::train()`. The default method for parameter selection criterion with 
is set to "CV" instead of the `caret::train()` default `boot`. The summary 
metric to used to select the optimal model is `RMSE` for continuous outcomes 
and `Accuracy` for categorical and binomial outcomes.

```{r carotene, eval = FALSE}
# I have no idea how to tune a neural net (or BART machine..) 
lrnr_caret_nnet <- make_learner(Lrnr_caret, algorithm = "nnet")
lrnr_caret_bartMachine <- make_learner(Lrnr_caret, algorithm = "bartMachine", 
                                       method = "boot", metric = "RMSE",
                                       tuneLength = 10)
```
In order to assemble the library of learners, we need to **"stack"** them
together.

A `Stack` is a special learner and it has the same interface as all
other learners. What makes a stack special is that it combines multiple learners
by training them simultaneously, so that their predictions can be either
combined or compared.

```{r stack}
stack <- make_learner(
  Stack,
  lrnr_glm, lrnr_mean, lrnr_ridge, lrnr_lasso, xgb_learners[[10]]
)
```

We can optionally select a subset of available covariates and pass only
those variables to the modeling algorithm.

Let's consider screening covariates based on their `randomForest` variable 
importance ranking (ordered by mean decrease in accuracy). 

```{r screener}
screen_rf <- make_learner(Lrnr_screener_randomForest, nVar = 5, ntree = 20)
# which covariates are selected on the full data?
screen_rf$train(washb_task)
```

To **"pipe"** only the selected covariates to the modeling algorithm, we need to
make a `Pipeline`, which is a just set of learners to be fit sequentially, where
the fit from one learner is used to define the task for the next learner.

```{r screener-pipe}
screen_rf_pipeline <- make_learner(Pipeline, screen_rf, stack)
```
Now our learners will be preceded by a screening step.

We also consider the original `stack`, to compare how the feature selection
methods perform in comparison to the methods without feature selection.

Analogous to what we have seen before, we have to stack the pipeline and
original `stack` together, so we may use them as base learners in our super
learner.

```{r screeners-stack, message=FALSE, warning=FALSE}
fancy_stack <- make_learner(Stack, screen_rf_pipeline, stack)
# we can visualize the stack
dt_stack <- delayed_learner_train(fancy_stack, washb_task)
plot(dt_stack, color = FALSE, height = "400px", width = "100%")
```

We will use the [default 
metalearner](https://github.com/tlverse/sl3/blob/master/R/default_metalearner.R), 
which uses [`Lrnr_solnp()`](https://github.com/tlverse/sl3/blob/master/R/Lrnr_solnp.R) 
to provide fitting procedures for a pairing of [loss 
function](https://github.com/tlverse/sl3/blob/master/R/loss_functions.R) and 
[metalearner 
function](https://github.com/tlverse/sl3/blob/master/R/metalearners.R). This
default metalearner selects a loss and metalearner pairing based on the outcome 
type. Note that any learner can be used as a metalearner.

We have made a library/stack of base learners, so we are ready to make the super 
learner. The Super Learner algorithm fits a metalearner on the validation-set 
predictions.

```{r make-sl, message=FALSE, warning=FALSE}
sl <- make_learner(Lrnr_sl,
  learners = fancy_stack
)
```
We can also use `Lrnr_cv` to build a Super Learner, cross-validate a stack of 
learners to compare performance of the learners in the stack, or cross-validate
any single learner (see "Cross-validation" section of this [`sl3` 
introductory tutorial](https://tlverse.org/sl3/articles/intro_sl3.html)).

Furthermore, we can [Define New `sl3` 
Learners](https://tlverse.org/sl3/articles/custom_lrnrs.html) which can be used 
in all the places you could otherwise use any other `sl3` learners, including
`Pipelines`, `Stacks`, and the Super Learner. 

```{r make-sl-plot, message=FALSE, warning=FALSE}
dt_sl <- delayed_learner_train(sl, washb_task)
plot(dt_sl, color = FALSE, height = "400px", width = "100%")
```

### 3. Train the Super Learner on the machine learning task {-}

The Super Learner algorithm fits a metalearner on the validation-set
predictions in a cross-validated manner, thereby avoiding overfitting. 

Now we are ready to **"train"** our Super Learner on our `sl3_task` object,
`washb_task`.

```{r sl}
sl_fit <- sl$train(washb_task)
```

### 4. Obtain predicted values {-}

Now that we have fit the Super Learner, we are ready to calculate the predicted
outcome for each subject.

```{r sl-predictions}
# we did it! now we have super learner predictions
sl_preds <- sl_fit$predict()
head(sl_preds)
```
<!--
Below we visualize the observed versus predicted values. 

For fun, we will also
include the cross-validated predictions from most popular learner on the block, 
main terms linear regression. 


```{r, plot-predvobs-woohoo}

df_plot <- data.frame(Observed = washb_data$whz, 
                      Predicted = sl_preds,
                      count = c(1:nrow(washb_data)))
                      
df_plot_melted <- melt(df_plot, 
                       id.vars = "count", 
                       measure.vars = c("Observed", "Predicted"))

ggplot(df_plot_melted, aes(value, count, color = variable)) + geom_point() 
```
-->
We can also obtain a summary of the results.

```{r, sl-summary}
sl_fit$print()
```

## Cross-validated Super Learner

We can cross-validate the Super Learner to see how well the Super Learner
performs on unseen data, and obtain an estimate of the cross-validated risk of
the Super Learner.

This estimation procedure requires an "external" layer of cross-validation,
also called nested cross-validation, which involves setting aside a separate
holdout sample that we don’t use to fit the Super Learner. This
external cross validation procedure may also incorporate 10 folds, which is the
default in `sl3`. However, we will incorporate 2 outer/external folds of
cross-validation for computational efficiency.

We also need to specify a loss function to evaluate Super Learner.
Documentation for the available loss functions can be found in the [`sl3` Loss
Function Reference](https://tlverse.org/sl3/reference/loss_functions.html).

```{r CVsl}
washb_task_new <- make_sl3_Task(
  data = washb_data,
  covariates = covars,
  outcome = outcome,
  folds = make_folds(washb_data, fold_fun = folds_vfold, V = 2)
)
CVsl <- CV_lrnr_sl(sl_fit, washb_task_new, loss_squared_error)
CVsl %>%
  kable(digits = 4) %>%
  kableExtra:::kable_styling(fixed_thead = T) %>%
  scroll_box(width = "100%", height = "300px")
```
<!-- Explain summary!!!! -->

## Variable Importance Measures with `sl3`

Variable importance can be interesting and informative. It can also be 
contradictory and confusing. Nevertheless, we like it, and so do 
collaborators, so we created a variable importance function in `sl3`! The `sl3` 
`varimp` function returns a table with variables listed in decreasing order of 
importance (i.e. most important on the first row). 

The measure of importance in `sl3` is based on a risk difference between the 
learner fit with a permuted covariate and the learner fit with the true 
covariate, across all covariates. In this manner, the larger the risk
difference, the more important the variable is in the prediction. 

Let's explore the `sl3` variable importance measurements for the `washb` data.

```{r varimp}
washb_varimp <- varimp(sl_fit, loss_squared_error)
washb_varimp %>%
  kable(digits = 4) %>%
  kableExtra:::kable_styling(fixed_thead = T) %>%
  scroll_box(width = "100%", height = "300px")
```

## Exercises

### Predicting Myocardial Infarction with `sl3` {#sl3ex1}

Follow the steps below to predict myocardial infarction (`mi`) using the
available covariate data. We thank Prof. David Benkeser at Emory University for
making the this Cardiovascular Health Study (CHS) data accessible.

```{r ex-setup, warning=FALSE, message=FALSE}
# load the data set
db_data <-
 url("https://raw.githubusercontent.com/benkeser/sllecture/master/chspred.csv")
chspred <- read_csv(file = db_data, col_names = TRUE)
# take a quick peek
head(chspred) %>%
  kable(digits = 4) %>%
  kableExtra:::kable_styling(fixed_thead = T) %>%
  scroll_box(width = "100%", height = "300px")
```

1. Create an `sl3` task, setting myocardial infarction `mi` as the outcome and
   using all available covariate data.
2. Make a library of seven relatively fast base learning algorithms (i.e., do
   not consider BART or HAL). Customize hyperparameters for one of your
   learners. Feel free to use learners from `sl3` or `SuperLearner`. You may
   use the same base learning library that is presented above.
3. Incorporate feature selection with the `SuperLearner` screener `screen.corP`.
4. Fit the metalearning step with the default metalearner.
5. With the metalearner and base learners, make the Super Learner and train it
   on the task.
6. Print your Super Learner fit by calling `print()` with `$`.
7. Cross-validate your Super Learner fit to see how well it performs on unseen
   data. Specify `loss_squared_error` as the loss function to evaluate the
   Super Learner.

### Predicting Recurrent Ischemic Stroke in an RCT with `sl3` {#sl3ex2}

For this exercise, we will work with a random sample of 5,000 patients who
participated in the International Stroke Trial (IST). This data is described in 
[Chapter 3.2 of the `tlverse` 
handbook](https://tlverse.org/tlverse-handbook/data.html#ist).

1. Train a Super Learner to predict recurrent stroke `DRSISC` with the available 
   covariate data (the 25 other variables). Of course, you can consider feature 
   selection in the machine learning algorithms. In this data, the outcome is 
   occasionally missing, so be sure to specify `drop_missing_outcome = TRUE` 
   when defining the task.
2. Use the SL-based predictions to calculate the area under the ROC curve (AUC).
3. Calculate the cross-validated AUC with cross-validated SL-based predictions. 
   If you would like to decrease the number of outer cross-validation folds, 
   then specify the task as described below for 5 outer folds. 

```{r ex-setup2, warning=FALSE, message=FALSE}
ist_data <- data.table(read.csv("https://raw.githubusercontent.com/tlverse/tlverse-handbook/master/data/ist_sample.csv"))

# number 3 help
ist_task_CVsl <- make_sl3_Task(
  data = ist_data,
  outcome = "DRSISC",
  covariates = colnames(ist_data)[-which(names(ist_data) == "DRSISC")],
  drop_missing_outcome = TRUE,
  folds = make_folds(
    n = sum(!is.na(ist_data$DRSISC)), 
    fold_fun = folds_vfold,
    V = 5
    )
  )
```

## Concluding Remarks

* The general ensemble learning approach of Super Learner can be applied to a
diversity of estimation and prediction problems that can be defined by a loss
function. 

* We just discussed conditional mean estimation, outcome prediction and 
variable importance. In future updates of the handbook, we will delve into 
prediction of a conditional density, and the optimal individualized treatment 
rule. 

* If we plug in the estimator returned by Super Learner into the target
  parameter mapping, then we would end up with an estimator that has the same
  bias as what we plugged in, and would not be asymptotically linear. It also 
  would not be a plug-in estimator or efficient. 
  
  + An asymptotically linear estimator is important to have, since 
  they converge to the estimand at $\frac{1}{\sqrt{n}}$ rate, and thereby permit 
  formal statistical inference (i.e. confidence intervals and $p$-values).
  + Plug-in estimators of the estimand are desirable because they respect both 
  the local and global constraints of the statistical model (e.g., bounds), and
  have they have better finite-sample properties. 
  + An efficient estimator is optimal in the sense that it has the lowest 
  possible variance, and is thus the most precise. An estimator is efficient if 
  and only if is asymptotically linear with influence curve equal to the 
  canonical gradient. The canonical gradient is a mathematical object that is 
  specific to the target estimand, and it provides information on the level of 
  difficulty of the estimation problem. The canonical gradient is shown in the 
  chapters that follow. Practitioner's do not need to know how to calculate a 
  canonical gradient in order to understand efficiency and use Targeted Maximum 
  Likelihood Estimation (TMLE). Metaphorically, you do not need to be Yoda in 
  order to be a Jedi.
  
* TMLE is a general strategy that succeeds in constructing efficient and 
  asymptotically linear plug-in estimators. 

* Super Learner is fantastic for pure prediction, and for obtaining an initial 
  estimate in the first step of TMLE, but we need the second step of TMLE to
  have the desirable statistical properties mentioned above. 

* In the chapters that follow, we focus on the targeted maximum likelihood
  estimator and the targeted minimum loss-based estimator, both referred to as
  TMLE.

## Appendix

### Exercise 1 Solution

Here is a potential solution to the [`sl3` Exercise -- Predicting Myocardial
Infarction with `sl3`](#sl3ex).

```{r ex-key, eval=FALSE, message=FALSE, warning=FALSE}
# make task
chspred_task <- make_sl3_Task(
  data = chspred,
  covariates = head(colnames(chspred), -1),
  outcome = "mi"
)

# make learners
glm_learner <- Lrnr_glm$new()
lasso_learner <- Lrnr_glmnet$new(alpha = 1)
ridge_learner <- Lrnr_glmnet$new(alpha = 0)
enet_learner <- Lrnr_glmnet$new(alpha = 0.5)
curated_glm_learner <- Lrnr_glm_fast$new(formula = "mi ~ smoke + beta + waist")
mean_learner <- Lrnr_mean$new() # That is one mean learner!
glm_fast_learner <- Lrnr_glm_fast$new()
ranger_learner <- Lrnr_ranger$new()
svm_learner <- Lrnr_svm$new()
xgb_learner <- Lrnr_xgboost$new()
screen_cor <- make_learner(Lrnr_screener_corP)
glm_pipeline <- make_learner(Pipeline, screen_cor, glm_learner)

# stack learners together
stack <- make_learner(
  Stack,
  glm_pipeline, glm_learner,
  lasso_learner, ridge_learner, enet_learner,
  curated_glm_learner, mean_learner, glm_fast_learner,
  ranger_learner, svm_learner, xgb_learner
)

# choose metalearner
metalearner <- make_learner(Lrnr_nnls)

sl <- Lrnr_sl$new(
  learners = stack,
  metalearner = metalearner
)
sl_fit <- sl$train(chspred_task)
sl_fit$print()

CVsl <- CV_lrnr_sl(sl_fit, chspred_task, loss_squared_error)
CVsl
```
